---
title: "SNCP Field Experiments"
subtitle: "2014 - 2017"  
author: "Chuck Lanfear"
date: 'Oct 26, 2018'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```


```{r xaringan-themer, include = FALSE}
library(xaringanthemer)

csss508css <- list(
     ".hljs-tomorrow-night-bright .hljs" = list(
        "background" = "#10102c",
        "border-radius"="5px"),
     ".remark-inline-code" = list(
        "background" = "#E0E0E0",
        "color" = "#10102c",
        "border-radius" = "3px",
        "padding" = "2px"),
     ".inverse .remark-inline-code" = list(
        "background" = "#10102c",
        "color" = "#ececf8",
        "border-radius" = "3px",
        "padding" = "2px"),
     ".small" = list("font-size" = "75%"),
     ".remark-code-line-highlighted" = list(
        "background-color" = "rgba(255,0,255,0.2)"),
     "sup" = list("font-size" = "14px"),
     "h1, h2, h3" = list(
        "margin-top"=".25em", 
        "margin-bottom"=".25em"),
     ".pull-left60" = list(
        "float" = "left",
        "width" = "58%" ),
     ".pull-right40" = list(
        "float" = "right",
        "width" = "38%" ),
     ".pull-right30" = list(
        "float" = "right",
        "width" = "30%" ),
     "a" = list("text-decoration" = "underline"),
     ".inverse a" = list("color" = "#cbd3a3"),
     "body" = list("line-height" = "1.4")
    )

mono_accent(base_color = "#342c5c",
            code_font_google = google_font("Fira Mono"),
            header_font_google = google_font("Quattrocento"),
            extra_css = csss508css,
            title_slide_background_image = "https://raw.githubusercontent.com/clanfear/CSSS508/master/Lectures/Week1/img/title_slide_img.png",
            title_slide_background_position = "bottom",
            title_slide_background_size = "contain"
)
```

Outline Slide

---

# Broken Windows

Wilson & Kelling (1982) describe a system where disorder (1) increases crime by 
signalling low social control and (2) decreases social control by reducing willingness to use public spaces.

.pull-left60[

![Broken Windows](https://clanfear.github.io/SocSem_102618/img/BWT.svg)

]

.pull-right40[

* Disorder signals low guardianship which increases offending.

* Disorder constrains social relations which impedes control.

* Social control inhibits both disorder and crime.
]

Reciprocal relationships 

---

# Collective Efficacy

Sampson & Raudenbush (1999) contend that disorder and crime are both manifestations of low social control.

.pull-left60[
![Broken Windows](https://clanfear.github.io/SocSem_102618/img/CE.svg)
]

.pull-right40[
* Disorder and crime are products of low social control.

* Disorder has no direct impact on crime or social control.
]



*These represent testable constraints on Broken Windows.*

---


