---
title: "SNCP Field Experiments"
subtitle: "2014 - 2017"  
author: "Chuck Lanfear"
date: 'Oct 26, 2018'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```


```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
library(dplyr)
library(ggplot2)

csss508css <- list(
     ".hljs-tomorrow-night-bright .hljs" = list(
        "background" = "#10102c",
        "border-radius"="5px"),
     ".remark-inline-code" = list(
        "background" = "#E0E0E0",
        "color" = "#10102c",
        "border-radius" = "3px",
        "padding" = "2px"),
     ".inverse .remark-inline-code" = list(
        "background" = "#10102c",
        "color" = "#ececf8",
        "border-radius" = "3px",
        "padding" = "2px"),
     ".small" = list("font-size" = "75%"),
     ".remark-code-line-highlighted" = list(
        "background-color" = "rgba(255,0,255,0.2)"),
     "sup" = list("font-size" = "14px"),
     "h1, h2, h3" = list(
        "margin-top"=".25em", 
        "margin-bottom"=".25em"),
     ".pull-left60" = list(
        "float" = "left",
        "width" = "58%" ),
     ".pull-right40" = list(
        "float" = "right",
        "width" = "38%" ),
     ".pull-right30" = list(
        "float" = "right",
        "width" = "30%" ),
     "a" = list("text-decoration" = "underline"),
     ".inverse a" = list("color" = "#cbd3a3"),
     "body" = list("line-height" = "1.4"),
     ".inverse" = list("background-image" = "url(https://clanfear.github.io/SocSem_102618/img/UWSocBG1_white.svg)")
    )

mono_accent(base_color = "#342c5c",
            code_font_google = google_font("Fira Mono"),
            header_font_google = google_font("Quattrocento"),
            extra_css = csss508css,
            background_image = "https://clanfear.github.io/SocSem_102618/img/UWSocBG1.svg"
)
```

# Outline

1. Theoretical Framework

2. Project Structure and Timeline

3. Experiments

   * Lost Letter
   * Mailbox Experiment
   * Littering Intervention
   * Litter Clean-Up
   
4. Synthesis


---
class: inverse

# Theoretical Framework 

---

# Broken Windows

Wilson & Kelling (1982) describe a system where disorder (1) increases crime by 
signalling low social control and (2) decreases social control by reducing willingness to use public spaces.

.pull-left60[

![Broken Windows](https://clanfear.github.io/SocSem_102618/img/BWT.svg)

]

.pull-right40[

* Disorder signals low guardianship which increases offending.

* Disorder constrains social relations which impedes control.

* Social control inhibits both disorder and crime.
]

Reciprocal relationships 

---

# Collective Efficacy

Sampson & Raudenbush (1999) contend that disorder and crime are both manifestations of low social control.

.pull-left60[
![Broken Windows](https://clanfear.github.io/SocSem_102618/img/CE.svg)
]

.pull-right40[
* Disorder and crime are products of low social control.

* Disorder has no direct impact on crime or social control.
]



*These represent testable constraints on Broken Windows.*


---
class: inverse

# Project Structure and Timeline

---

This project links field experiments embedded in Seattle neighborhoods 
to data from the 2002-2003 Seattle Neighborhoods and Crime Survey.

Our goal is estimation of the parameters that connect disorder, 
crime, and social control.

ANNOTATED IMAGE HERE
Depicts where each experiment fits in

---

```{r, echo=FALSE, message=FALSE, warning=FALSE, dev='svg'}
exp_df <- expand.grid(year = 2014:2017,
                      experiment = c("Lost Letter", "Mailbox", "Littering\nIntervention", "Litter\nClean-Up")) %>%
  mutate(active = case_when(
    experiment=="Mailbox" ~ 1,
    experiment=="Lost Letter" & year==2015 ~ 1,
    experiment=="Littering\nIntervention" & year==2017 ~ 1,
    experiment=="Litter\nClean-Up" & year==2017 ~1,
    TRUE ~ 0
  ), trials = case_when(
    experiment=="Mailbox" & year==2014 ~ 130,
    experiment=="Mailbox" & year==2015 ~ 141,    
    experiment=="Mailbox" & year==2016 ~ 104,
    experiment=="Mailbox" & year==2017 ~ 114,
    experiment=="Lost Letter" & year==2015 ~ 2938,
    experiment=="Littering\nIntervention" & year==2017 ~ 568,
    experiment=="Litter\nClean-Up" & year==2017 ~ 21,
    TRUE ~ as.numeric(NA)
)) %>%
  mutate(experiment = forcats::fct_relevel(experiment, "Litter\nClean-Up", "Littering\nIntervention", "Mailbox", "Lost Letter"))

ggplot(exp_df, aes(x=year, y=experiment, fill=factor(active))) + 
  xlab("") + ylab("") + ggtitle("Experiment Timeline", subtitle= "Number of trials") + 
  geom_tile() + 
    geom_text(size=6, color="#cbd3a3", hjust=0.5, aes(label=trials)) +
  scale_fill_manual(values=c("1" = "#342c5c", "0" = "white")) +
  theme_minimal(base_size=21) + 
  theme(legend.position = "none", axis.text.x = element_text(angle=45, hjust=1),
        axis.text.y = element_text(hjust = 0.5),
        panel.grid = element_blank())
```